other functionalities

### 2022-09-20 inst/gitbook/05_other-functionalities.Rmd
added MCMCglmm.variance and updates on randtest.dispRity

Since version `1.7`, the `dispRity` package contains several utility functions for manipulating `"MCMCglmm"` (that is, objects returned by the function `MCMCglmm::MCMCglmm`).
These objects are a modification of the `mcmc` object (from the package `coda`) and can be sometimes cumbersome to manipulate because of the huge amount of data in it.
You can use the functions `MCMCglmm.traits` for extracting the number of traits, `MCMCglmm.levels` for extracting the level names, `MCMCglmm.sample` for sampling posterior IDs and `MCMCglmm.covars` for extracting variance-covariance matrices.

@@

## Extracting these two random amples
my_covars <- MCMCglmm.covars(my_MCMCglmm, sample = random_samples)
```

>>>>

Since version `1.7`, the `dispRity` package contains several utility functions for manipulating `"MCMCglmm"` (that is, objects returned by the function `MCMCglmm::MCMCglmm`).
These objects are a modification of the `mcmc` object (from the package `coda`) and can be sometimes cumbersome to manipulate because of the huge amount of data in it.
You can use the functions `MCMCglmm.traits` for extracting the number of traits, `MCMCglmm.levels` for extracting the level names, `MCMCglmm.sample` for sampling posterior IDs and `MCMCglmm.covars` for extracting variance-covariance matrices. You can also quickly calculate the variance (or relative variance) for each terms in the model using `MCMCglmm.variance` (the variance is calculated as the sum of the diagonal of each variance-covariance matrix for each term).

@@

## Extracting these two random samples
my_covars <- MCMCglmm.covars(my_MCMCglmm, sample = random_samples)

## Plotting the variance for each term in the model
boxplot(MCMCglmm.variance(my_MCMCglmm), horizontal = TRUE, las = 1,
        xlab = "Relative variance",
        main = "Variance explained by each term")
```
